Real estate is a crucial component of any economy, serving as both an asset and a key driver of economic growth. The value of real
estate is determined by a variety of factors, including location, condition, and demand. Analyzing the factors that contribute to
the value of real estate and the growth of that value can provide insights into the economic health of a region and inform
investment decisions. The Real Estate Valuation Data Set provides a rich source of information for studying the factors that
influence the value of real estate. The data set includes information on the sale price (in NT\$10000 per ping, where 1 ping is
equal to 3.3 squared meters) of real estate properties in Taiwan, as well as a variety of features such as the age of property (in
years), the distance to the nearest MRT station (in meters), the number of convenience stores in the surrounding area, as well as
location data (longitude and latitude in degrees). The data set also includes information on the transaction date, allowing for
temporal analysis of real estate trends. This project aims to analyze the Real Estate Valuation Dataset to provide investment
advice on where in the region to purchase real estate based on which factors of real estate in this region are associated with
higher growth in price over time. We will do this by engineering many variables and interactions, and investigating which
variables, when multiplied by date, are useful predictors of price, as this would indicate which properties may be worth more when
sold in the future.
